Predicting Covid Data

### 2022-12-04 jin_sim.Rmd
Added China analysis to main.

```{r}
gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
summary(model1)
model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
summary(model2)
```

>>>>

```{r}
gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
summary(model1)$parameters
model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
summary(model2)$parameters
```

### 2022-12-04 main.rmd
Added China analysis to main.

---
title: "Predicting Covid Data"
author: Austin Lackey, Chien Lin and Jin Peng
date: Tuesday, November 6th, 2022
output: powerpoint_presentation
---

@@

## China Simulation

>>>>

---
title: "Predicting Covid Data"
author: "Austin Lackey, Chien Lin and Jin Peng"
date: "Tuesday, November 6th, 2022"
output:
  powerpoint_presentation: default
  beamer_presentation: default
---

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# useful libraries
library(tidyverse)
library(dplyr)
library(ggplot2)
library(pracma)
# read covid data
data <- read_csv("owid-covid-data.csv")
```

@@

## Available Official Data

Cumulative diagnosed positive cases:

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold", out.width="50%"}
# extract China data of interest
china <- data |>
  filter(location == "China") |>
  filter(date >= "2020-01-22", date <= "2020-03-28") |>
  select(c(date, total_cases, total_deaths)) |>
  mutate(days = 1:n())

# recreate plots
positive <- ggplot(data = china) +
  geom_point(aes(x = days, y = total_cases), color = "red") +
  labs(x = "Days", y = "China cumulative number of cases")
positive
```

## Available Official Data

Cumulative fatalities:

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold", out.width="50%"}
fatalities <- ggplot(data = china) +
  geom_point(aes(x = days, y = total_deaths), color = "red") +
  labs(x = "Days", y = "China cumulative number of fatalities") +
  ylim(0,5000)
fatalities
```

## Fit by the Gauss Error Function

Apply $nls$ function to determine the nonlinear (weighted) least-squares estimates of the four parameters $a,b,c,d$ of a Gauss error function model: $a+b*erf(c*x-d)$.

```{r, include=FALSE, message=FALSE, warning=FALSE}
gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
```

```{r, message=FALSE, warning=FALSE}
model <- nls(total_cases ~ gauss_fn(days,a,b,c,d), 
             data=china, 
             start=list(a=10000,b=10000,c=0.1,d=1))
```

## Fit by the Gauss Error Function

Fit of cumulative diagnosed positive cases:

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
summary(model1)$parameters
fn_model1 <- function(x) {4.017e+04 + 4.047e+04 * erf(9.284e-02 * x - 1.732e+00)}
positive + stat_function(fun=fn_model1, color="blue")
```

## Fit by the Gauss Error Function

Fit of cumulative fatalities:

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
#summary(model2)$parameters
fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
fatalities +
  stat_function(fun=fn_model2, color="blue")
```
